Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-25 paper/paper.tex
table 2 missing categories

    JBoss JMX\MyComment{ Console Beanshell Exploit} & RCE & HTTP \MyComment{& Remote Code Execution} & \textbf{content}:"/HtmlAdaptor"; nocase; http\_uri; \textbf{content}:"action=inspect"; nocase; http\_uri; \textbf{content}:"bean"; nocase; http\_uri; \textbf{content}:"name="; http\_uri; \\
    WeBid \MyComment{Local File Inclusion} & - & TCP \MyComment{& Local File Inclusion} & \textbf{content}:"GET "; depth:4; \textbf{content}:"/cron.php?"; http\_uri; nocase; \textbf{content}:"include\_path="; http\_uri; nocase; \textbf{content}:"../"; \\
    ColdFusion \MyComment{Privilege Escalation} & - & HTTP \MyComment{& Privilege Escalation} & \textbf{content}:"GET"; http\_method; nocase; \textbf{content}:"/CFIDE/administrator"; http\_uri; nocase; \\
    .htaccess access\MyComment{attempted-recon} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".htaccess"; nocase; http\_uri; \\
    .idq access\MyComment{EXPLOIT ISAPI} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".idq"; nocase; http\_uri; \\
    iisadmin access\MyComment{web-application-attack} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/iisadmin"; nocase; http\_uri; \\
    /system32/ in URI\MyComment{Possible Protected Directory Access Attempt} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/system32/"; nocase; http\_uri; \\
    Script tag in URI\MyComment{Possible Cross Site Scripting Attempt} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"</script>"; nocase; http\_uri; \\
    \bottomrule
  \end{tabular}
\end{table*}

@@

\subsubsection{Malicious traffic.}To reproduce the malicious traffic
for http and tcp attacks, we configured an http server (Apache2) in
one machine and Nikto2~\cite{nikto} in a different machine. Nikto is
an open source tool with a catalog of scripts to reproduce
vulnerabilities. It is important to note that this setup is \emph{not}
necessary if \emph{pcap} files---pcap is the input format used by
\tname{}---for the attack already exist. As explained in
Section~\ref{sec:minimization}, pcap files abstract network
messages~\cite{pcap} and can be used to avoid network traffic during
rule synthesis. We proceeded as follows to obtain pcap files for the
the attacks we analyzed: we 1)~instantiated the script (\eg{}, defined
the IP of the web server), 2)~executed the Nikto2 script, 3)~and
monitored the traffic with the Wireshark network
monitor~\cite{wireshark-net-monitor}. The Wireshark tool records the
traffic and reports pcap files on output for replaying. The only
difference in the setup of non-http non-tcp attack is in the first
step of this procedure. For example, we used the hping3~\cite{hping3}
command to reproduce the ICMP SYN Flood attack: \CodeIn{hping3 -d 80
  -w 64 -S -p 80 --flood --rand-source <IP>}. This command alone
reproduces a flooding attack on a given machine
(Section~\ref{sec:dos}).\Mar{what about the variants? where do they
  come from? this is confusing as the narrative above suggests the
  attack is hardcoded in the tool.}

>>>>

    JBoss JMX\MyComment{ Console Beanshell Exploit} & RCE & HTTP \MyComment{& Remote Code Execution} & \textbf{content}:"/HtmlAdaptor"; nocase; http\_uri; \textbf{content}:"action=inspect"; nocase; http\_uri; \textbf{content}:"bean"; nocase; http\_uri; \textbf{content}:"name="; http\_uri; \\
    WeBid \MyComment{Local File Inclusion} & RFI & TCP \MyComment{& Local File Inclusion} & \textbf{content}:"GET "; depth:4; \textbf{content}:"/cron.php?"; http\_uri; nocase; \textbf{content}:"include\_path="; http\_uri; nocase; \textbf{content}:"../"; \\
    ColdFusion \MyComment{Privilege Escalation} & Privilege Escalation & HTTP \MyComment{& Privilege Escalation} & \textbf{content}:"GET"; http\_method; nocase; \textbf{content}:"/CFIDE/administrator"; http\_uri; nocase; \\
    .htaccess access\MyComment{attempted-recon} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".htaccess"; nocase; http\_uri; \\
    .idq access\MyComment{EXPLOIT ISAPI} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".idq"; nocase; http\_uri; \\
    iisadmin access\MyComment{web-application-attack} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/iisadmin"; nocase; http\_uri; \\
    /system32/ in URI\MyComment{Possible Protected Directory Access Attempt} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/system32/"; nocase; http\_uri; \\
    Script tag in URI\MyComment{Possible Cross Site Scripting Attempt} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"</script>"; nocase; http\_uri; \\
    \bottomrule
  \end{tabular}
\end{table*}

@@

\subsubsection{Malicious traffic.}To reproduce the malicious traffic
for http and tcp attacks, we configured an http server (Apache2) in
one machine and Nikto2~\cite{nikto} in a different machine. Nikto is
an open source tool with a catalog of scripts to reproduce
vulnerabilities. It is important to note that this setup is \emph{not}
necessary if \emph{pcap} files---pcap is the input format used by
\tname{}---for the attack already exist. As explained in
Section~\ref{sec:minimization}, pcap files abstract network
messages~\cite{pcap} and can be used to avoid network traffic during
rule synthesis. We proceeded as follows to obtain pcap files for the
the attacks we analyzed: we 1)~instantiated the script (\eg{}, defined
the IP of the web server), 2)~executed the Nikto2 script, 3)~and
monitored the traffic with the Wireshark network
monitor~\cite{wireshark-net-monitor}. The Wireshark tool records the
traffic and reports pcap files on output for replaying. The only
difference in the setup of non-http non-tcp attack is in the first
step of this procedure. For example, we used the hping3~\cite{hping3}
command to reproduce the ICMP SYN Flood attack: \CodeIn{hping3 -d 80
  -w 512 -S -p 80 --flood --rand-source <IP>}. This command alone
reproduces a flooding attack on a given machine
(Section~\ref{sec:dos}).\Mar{what about the variants? where do they
  come from? this is confusing as the narrative above suggests the
  attack is hardcoded in the tool.}
